Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope

### 2021-11-03 roman_metacal.tex
updates

In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below. (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. These shear biases arise for various reasons. For space-based surveys, it can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying these biases before the real survey is extremely important. \par

@@

\begin{table*}
	\centering
	\label{tab:bias_summary}
	\begin{tabular}[scale=1.4]{ c|c|c|c|c } 
		\hline
		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
		\hline
		\textcolor{red}{single-epochs (J129; w/ noise fix)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
		\textcolor{red}{single-epochs (F184)} & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
		\textcolor{red}{single-epochs (H158; w/ noise fix)} & -1.18$\pm$0.63 & -1.43$\pm$0.67 & 2.14$\pm$1.35 & 1.83$\pm$1.19\\
		\hline
		\textcolor{red}{single-band coadd with oversampling (H158; w/ noise fix)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
		\textcolor{red}{single-band coadd with oversampling (J129 w/ noise fix)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
		\textcolor{red}{single-band coadd with oversampling (F184 w/ noise fix)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
		\hline
		\textcolor{red}{multiband single-epochs (gauss) (H158+J129+F184)} & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
		\textcolor{red}{multiband coadd (w/ noise fix)} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\

>>>>

In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below. (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. The bias arises for various reasons. For space-based surveys, the bias can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying these biases before the real survey is extremely important. \par

@@

\begin{table*}
	\centering
	\label{tab:bias_summary}
	\begin{tabular}[scale=1.4]{ c|c|c|c|c } 
		\hline
		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
		\hline
		\textcolor{red}{single-epochs (J129)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
		single-epochs (F184) & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
		single-epochs (H158) & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
		\hline
		\textcolor{red}{single-band coadd with oversampling (H158; w/ noise fix)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
		\textcolor{red}{single-band coadd with oversampling (J129 w/ noise fix)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
		\textcolor{red}{single-band coadd with oversampling (F184 w/ noise fix)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
		\hline
		\textcolor{red}{multiband single-epochs (gauss) (H158+J129+F184)} & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
		\textcolor{red}{multiband coadd (w/ noise fix)} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
